\section{Discussion and Sources of Error}
Using an IC 741 op-amp, we have successfully constructed inverting and non-inverting amplifier setups and measured their gain values. In case of an inverting amplifier, there is about 0.2\% and 0.4\% deviation of the experimental value from the theoretical value for each set of $R_f$ and $R_\text{in}$ respectively. For the non-inverting setup, the deviations were 0.4\% and 1.7\% respectively. These deviations could be due ito error in the measurement of resistance, error stemming from assumption of an ideal op-amp or due to small capacitances builing up at the metal junctions in the circuit.

Additionally, we have also demonstrated op-amp as a summing and difference amplifier. While the difference in theoretical and experimental values in the case of the summing amplifier was at most $\pm$0.06 V, the same for the difference amplifier was 0.035V to 0.194V. Since, there is no ideal op-amp in real life, the deviations could be due to a multitude of factors including common-mode gain, offset voltage, noise or due to supply voltage fluctuations. 

We have also used the op-amp to build a comparator circuit with and without threshold voltage as demonstrated in Fig. \ref{g3}. Similarly we have built a schmitt trigger circuit which was able to show hysteresis as shown in Fig. \ref{g4} and Fig. \ref{g5}. 

\section{Precautions}

\begin{enumerate}
    \item The power supply to the operational amplifier never becomes reversed in polarity.
    \item Make sure the connections are proper before switching on the circuit.
\end{enumerate}

\section{Conclusion}
We have demonstrated basic op-amp configurations, including inverting and non-inverting amplifiers, and its application as a summing amplifier, a difference amplifier, a comparator and a Schmitt trigger.

\section{Applications}
Op-amps have a broad range of usages, and as such are a key building block in many analog applications — including filter designs, voltage buffers, comparator circuits,