\section{Procedure}

\begin{enumerate}
    \item Turn on the Helmoltz Coil power supply and set
    the current to 150 mA.
    \item Configure the ESR Spectrometer front panel
    controls as follows -- Frequency: Centered, Phase: Centered.
    \item On the CRO (Cathode Ray Oscilloscope) screen, operating in XY mode, observe four peaks. Adjust the FREQUENCY of the Spectrometer and the SENSITIVITY of the CRO to achieve optimal results, ensuring sharp peaks and a good signal-to-noise ratio.
    \item Use the PHASE knob to align the two pairs of
    peaks as closely as possible.
    \item Adjust the orientation of the Helmholtz coils
    relative to the main unit to achieve the best
    overlap of the baselines.
    \item Adjust the horizontal sensitivity of the oscilloscope to the
    maximum. The X-axis of the oscilloscope represents the constant AC voltage supplied by the
    ESR spectrometer for measurement purposes.
    \item Measure the total
    display on the X-axis, denoted as 'P' divisions
    of the CRO X plate. Note that the zero field is
    located at the middle point of the X-axis.
    \item Adjust the frequency, detection level, and vertical sensitivity
    of the oscilloscope to obtain the best possible
    resonance peaks, while keeping the current fixed
    at 150 mA.
    \item Fix the frequency and vary the current
    flowing through the coils. Measure the corresponding horizontal separation between the two
    resonance peaks ($2Q$) after adjusting the phase.
    Take five to six sets of observations by varying
    the current.
    \item Use the provided A.C. Gauss meter to measure the A.C.
    r.m.s magnetic field (H) corresponding to the
    currents used in the previous step.
    \item Measure
    the gap between the positions of the two peaks
    ($2Q$). Ensure that these peaks are equidistant
    from the middle point (denoted as $Q$ divi-
    sions). Calculate Q from the measured
    value of $2Q$ by dividing $2Q$ by $2$.
    \item Calculate $H_{pp}$ (Peak-to-peak
    magnetic field), $H_0$ (static magnetic field), and $g$ (Lande factor).
    \item Repeat the experiment using different frequencies,
    following the same procedure for each frequency

\end{enumerate}