\section{Results and Discussion}
We have successfully constructed CE and CB modes using a NPN and PNP transistor respectively. From analysing voltage and current in the circuit, we were able to study the following characteristics.

\subsection*{For an NPN transistor in CE mode}
From Fig. \ref{graph:1}, we can observe that when the input voltage $V_{BE}$ is increased initially there is no current produced, further when it is increased the input current $I_B$ increases steeply. When the output voltage $V_{CE}$ is further increased the curve shifts right side, i.e., higher value of $V_{BE}$ is required to activate the transistor.

The output characteristics show that initially for very small values of $V_{CE}$, $I_C$ increases almost linearly. When $V_{CE}$ is more than that required to reverse bias the base-collector junction, $I_C$ increases very little with $V_{CE}$. 
    
Here by plotting $I_C$ vs $V_{CE}$ for fixed values of $I_B$, (Fig. \ref{graph:2}) we can see that, for a fixed value of $V_{CE}$, $I_B$ increases with $I_C$.

Furthermore, the current amplification factor was found to be, $\beta=154.78$.

\subsection*{For a PNP transistor in CB mode}
From Fig. \ref{graph:4}, we can observe that when the input voltage $V_{EB}$ is increased initially there is no current produced, further when it is increased the input current $I_E$ increases steeply. When the output voltage $V_{CB}$ is further increased the curve shifts left side, i.e., lower value of $V_{EB}$ is required to activate the transistor.

Furthermore, output characteristics show that initially for very small values of $V_{CB}$, $I_C$ increases almost linearly. When $V_{CB}$ is more than that required, $I_C$ increases very little with $V_{CB}$. We can also see that the maximum value $I_C$ increases with $I_E$.

The current amplification factor, was found to be $\alpha=1.02$.

\section{Precautions}
\begin{enumerate}
    \item Verify that the multimeters are in working condition before starting the experiment.
    \item Switch on the circuit only after verifying the connections to be proper.
    \item Do not change the any components on the circuit while the circuit is switched on.
\end{enumerate}