\section{Error Analysis}
From Eqn. (6), uncertainity in $f_o$ would be,

\begin{align*}
    \Delta f_o &= f_o\sqrt{\left(\frac{\Delta L}{2L}\right)^2 + \left(\frac{\Delta C}{2C}\right)^2}\\
    &=19.574\cdot\sqrt{\left(\frac{0.1}{2\cdot952.4}\right)^2 + \left(\frac{0.01}{2\cdot75.41}\right)^2}\\
    &=0.001
\end{align*}

And, from Eqn. (8), uncertainity in $Q$ will be,

\begin{align*}
    \Delta Q = Q&\sqrt{\left(\frac{\Delta f_o}{f_o}\right)^2 + \left(\frac{\Delta L}{L}\right)^2 + \left(\frac{\Delta R_{dc}}{R_{dc}}\right)^2}\\
    \implies \Delta Q_1&=0.0005\text{ and }\Delta Q_1=0.003
\end{align*}

where $R_{dc}$ is the sum of resistance of the resistor, inductor and the output impedance of the function generator.

\section{Results and Discussion}
We have studied the properties of a series LCR circuit by measuring voltage across different junctions against various input frequencies. The calculated values of resonance frequency of the circuit is (19.574 $\pm$ 0.001) kHz.\\

At resonance, we have found out that,

\begin{itemize}
    \item $V_R/V_i$ is maximum, i.e. the circuit is purely resistive. And therefore $\phi_R=0^{\circ}$. (Hence, $f_o=19.78$ kHz).
    \item $V_{LC}$ is minimum and $\phi_{LC}$ is close to $90^{\circ}$. (Hence, $f_o=20.00$ kHz).
    \item since the capacitor attenuates high frequency signal and the inductor attenuates low frequency signal, at resonance $V_L = V_C$. (Hence, $f_o=20.30$ kHz).\\
\end{itemize}

The observed values of the resonance frequency from the plots obtained closely match the calculated value, and the average observed value of the resonance frequency is $f_o=20.03$.

We have also found out the Quality factor of the circuit, which comes out to be $Q=(0.773\pm0.0005)$ when $R=98.4\,\Omega$ and $Q=(1.098\pm0.003)$ when $R=46.2\,\Omega$. Graphically, the corresponding values of Q-factor are 0.881 and 1.547 respectively.

So, one can conclude that resistive energy loss will be lower in the second cicuit, and it will have better selectivity (narrow bandwidth or a sharper resonance).

\section{Precautions}
\begin{enumerate}
    \item Make the ground connections carefully.
    \item Take readings only when the values on the oscilloscope stabilize.
    \item Do not change any component of the circuit while it is switched on.
\end{enumerate}